Neural Networks as Dual Gaussian Processes for Sequential Learning

### 2023-09-18 papers/iclr-2024/main.tex

    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT
	\input{tables/uci.tex}
\end{table}

\begin{figure}[t]
  \centering\scriptsize
  \setlength{\figurewidth}{.26\textwidth}
  \setlength{\figureheight}{\figurewidth}
  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\footnotesize},y tick label style={font=\footnotesize},title style={yshift=-4pt,font=\large}, y label style={font=\large},x label style={font=\large},grid=major, width=\figurewidth, height=\figureheight}
  \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
  \pgfplotsset{xlabel={$M$},ylabel style={yshift=-12pt}}
  %
  \begin{minipage}[t]{.17\textwidth}
    \raggedleft
    \pgfplotsset{ylabel=NLPD}
    \input{./fig/australian.tex}
  \end{minipage}
  \hfill
%  \begin{minipage}[t]{.16\textwidth}
%    \raggedleft
%    \input{./fig/breast_cancer.tex}
%  \end{minipage}
%  \hfill
%  \begin{minipage}[t]{.16\textwidth}
%    \raggedleft
%    \input{./fig/ionosphere.tex}
%  \end{minipage}
%  \hfill
  \begin{minipage}[t]{.16\textwidth}
    \raggedleft
    \input{./fig/glass.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.16\textwidth}
    \raggedleft
    \input{./fig/vehicle.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.16\textwidth}
    \raggedleft
    \input{./fig/waveform.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.16\textwidth}
    \raggedleft
    \input{./fig/digits.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.16\textwidth}
    \raggedleft
    \input{./fig/satellite.tex}
  \end{minipage}\\[-1em]
  %
  % Legend
  \definecolor{steelblue31119180}{RGB}{31,119,180}
  \definecolor{darkorange25512714}{RGB}{255,127,14}
  \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean over 10 seeds) on UCI classification tasks: \our (thick) vs.\ subsets (\cite{immer2021improving}, thin). Orange lines (\myline{darkorange25512714}) use the GP mean, whereas blue lines (\myline{steelblue31119180}) the NN MAP estimate as mean. Our \our converges fast for all cases.\looseness-1}
  \label{fig:uci}
  %\vspace*{-6pt}
\end{figure}

>>>>

    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT
	\input{tables/workshop_uci_table.tex}
\end{table}

\begin{figure*}[t]
  % \centering\scriptsize
  \centering\small
  % \setlength{\figurewidth}{.18\textwidth}
  \setlength{\figurewidth}{.27\textwidth}
  \setlength{\figureheight}{\figurewidth}
  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\Large},y tick label style={font=\Large},title style={yshift=-4pt,font=\LARGE}, y label style={font=\Large},x label style={font=\LARGE},grid=major, width=\figurewidth, height=\figureheight}
  \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
  \pgfplotsset{xlabel={$M$ as \% of $N$},ylabel style={yshift=-5pt},xlabel style={yshift=-5pt}}
  %
  \begin{minipage}[t]{.175\textwidth}
    \raggedleft
    \pgfplotsset{ylabel=NLPD}
    \input{./fig/australian.tex}
  \end{minipage}
  \hfill
  % \begin{minipage}[t]{.12\textwidth}
  %   \raggedleft
  %   \input{./fig/breast_cancer.tex}
  % \end{minipage}
  % \hfill
  % \begin{minipage}[t]{.12\textwidth}
  %   \raggedleft
  %   \input{./fig/ionosphere.tex}
  % \end{minipage}
  % \hfill
  \begin{minipage}[t]{.155\textwidth}
    \raggedleft
    \input{./fig/glass.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.155\textwidth}
    \raggedleft
    \input{./fig/vehicle.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.155\textwidth}
    \raggedleft
    \input{./fig/waveform.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.155\textwidth}
    \raggedleft
    \input{./fig/digits.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.155\textwidth}
    \raggedleft
    \input{./fig/satellite.tex}
  \end{minipage}\\[-1em]
  %
  % Legend
  \definecolor{steelblue31119180}{RGB}{31,119,180}
  \definecolor{darkorange25512714}{RGB}{255,127,14}
  \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean\textcolor{gray}{\footnotesize$\pm$std} over 5 seeds) on UCI classification tasks: \our (\myline{steelblue31119180}) vs. GP subset (\myline{darkorange25512714}). Our \our converges fast for all cases showing clear benefits of its ability to summarize all the data onto a sparse set of inducing points. The number of inducing points $M$ are specified as a percentage of the number of training data $N$.}
  \label{fig:uci}
  %\vspace*{-6pt}
\end{figure*}
